MFCCs, Chroma Features, and Spectrogram Images for Deepfake Audio Classification Using Machine Learning

### 2024-12-04 paper/paper.tex
added a few more headers
final mfcc paragraph revisions

Generating a vector of MFCC features was an essential step in our preprocessing efforts. In our experiments, we used a sampling rate of 22050 Hz, which resulted in 20 features for each audio sample. These features were then saved to a CSV file, making them available for later model training. These features played a pivotal role in the model's ability to make accurate decisions.

\subsection{Mel-Spectrogram Images}
Nora TODO
\subsection{Convolutional Neural Networks}
Nora TODO
\subsubsection{VGG16}
Nora TODO
\subsubsection{ResNet50}
Nora TODO
\section{Methodology}

@@

>>>>

Generating a vector of MFCC features was an essential step in our preprocessing efforts. A sample rate of 44100 Hz corresponding to a maximum sound frequency of 22050 Hz is usually used for recording sound, because a human can hear sounds ranging from 20 Hz to 20000 Hz \cite{9252126}. In our experiments, we used a sampling rate of 22050 Hz. This is half of the common sample rate for recording sound, and is a common value for sampling rate when generating MFCCs. This resulted in 20 features for each audio sample. These features were then saved to a CSV file, making them available for later model training. These features played a pivotal role in the model's ability to make accurate decisions.

\subsection{Mel-Spectrogram Images}
Nora TODO
\subsection{Convolutional Neural Networks}
Nora TODO
\subsubsection{VGG16}
Nora TODO
\subsubsection{ResNet50}
Nora TODO

\subsection{Chroma Features}

\section{Methodology}

@@

\subsection{for-original dataset}

\subsection{for-norm dataset}

\subsection{for-2sec dataset}

\subsection{for-rerec dataset}
